%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Pprofessor, Master in GIS} % Job title
    {Universidad de Costa Rica} % Organization
    {Montes de Oca, Costa Rica} % Location
    {First Semester 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Professor of Course PF-0903 Spatial Database Design and Exploration
      \end{cvitems}
    }
  \cventry
    {Lead Geospatial Data Analyst} % Job title
    {SOLTIG S.A.} % Organization
    {Alajuela, Costa Rica} % Location
    {2019 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Geographic Information Systems (GIS) Administrator.
        \item Data apps and dashboards developer with Streamlit.
        \item Spatial Database Administrator in Microsoft Azure.
        Database for PostgreSQL.
        \item Microsoft Azure Administrator.
        \item Professor of courses of: Free GIS (QGIS), ODM, Geostatistics, PyQGIS,
        Image classifications, Spatial Data Infrastructure.
        (PostgreSQL / PostGIS GeoServer).
        \item Solutions Architect.
        \item Commercial support technician for projects and sales of solutions.
        solutions.
        \item Innovation Manager.
      \end{cvitems}
    }
  \cventry
    {GIS Analyst} % Job title
    {SOLTIG S.A.} % Organization
    {Alajuela, Costa Rica} % Location
    {2016 - \textit{2019}} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Geographic Information Systems (GIS) Administrator.
        \item Instructor of courses of: Free GIS (QGIS), ODM, QFiled, Geostatistics,
        Image processing, Spatial Data Infrastructure.
        (PostgreSQL / PostGIS GeoServer).
        \item Technical sales support for projects and solutions.
        solutions.
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
\newpage