%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Programs and Certifications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
  {Microsoft Certified: Azure Fundamentals} % Affiliation/role
    {Microsoft Certifications} % Organization/group
    {Microsoft} % Location
    {2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Foundational knowledge of cloud concepts in general and Azure in
              particular.
        \item Describe cloud concepts
        \item Describe Azure architecture and services
        \item Describe Azure management and governance
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  {Getting started with Python} % Affiliation/role
    {LinkedIn} % Organization/group
    {LinkedIn Learning} % Location
    {2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Datas structures.
        \item Software Development.
        \item Python.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Machine Learning Certificate 6.0 CU} % Affiliation/role
    {Texas Tech University} % Organization/group
    {Texas Tech University - Costa Rica} % Location
    {2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Machine Learning Fundamentals: Python and Scikit-Learn.
        \item Deep Learning: Deep Neural Networks with TensorFlow and Keras.
        \item Natural Language Processing: TensorFlow and NLTK.
        \item Unsupervised Machine Learning: Scikit-learn and TensorFlow.
        \item Reinforcement Learning: TensorFlow, OpenAI GYM and TF-Agents.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
  {Innovation Manager} %Affiliation/role
    {Practical Training Program in Market-Oriented Innovation} % Organization/role
    {UTN Costa Rica - University of Leipzig Germany} % Location
    {2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item Specialization program in Market Focused Innovation.
        \item Market-focused innovation specialization program.
        \item Training in the leadership of Innovation Projects and Processes.
        and Innovation Processes.
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
