%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
  {Lead Geospatial Data Analyst} % Job title
  {CONARE: Electoral Geography} % Organization
  {Countrywide, Costa Rica} % Location
  {2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Development of the data analysis model with PySAL.
      \item Exploratory analysis of spatial data.
      \item Analysis of spatial autocorrelation of electoral data.
      with I de Mora Local.
      \item Creation of maps for CONARE's State of the Nation Report 2023.
    \end{cvitems}
  }
%---------------------------------------------------------
\cventry
  {Lead Geospatial Data Analyst} % Job title
  {CCSS Hospital Mexico: Database development and spatial data analysis} % Organization
  {Countrywide, Costa Rica} % Location
  {2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Development of ETL process for the integration of multiple data sources.
      \item Data warehouse and data wrangling.
      \item Processing of 6 million infectious disease outcome data.
      \item Spatial analysis of 6 million data from all H. Mexico laboratory tests to
      discover epidemiological trends. to discover epidemiological trends and infection
      foci from 2005 to 2021. from 2005 to 2021.
      \item Development of dashboard with Power BI and QGIS for data analysis by H. Mexico
      physicians. by the physicians of H. Mexico.
      \item Presentation of results to the research committee of the Centro de
      Strategic Development and Information in Health and Social Security.
    \end{cvitems}
  }
%---------------------------------------------------------
\cventry
  {Leading Data Analyst} % Job title
  {CNFL Communication Perception Study} % Organization
  {GAM, Costa Rica} % Location
  {2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Methodological design of the project.
      \item Quality assurance.
      \item Spatial data analysis using QGIS.
      \item Development of QGIS course for CNFL.
      \item Support for the development of a dashboard with PowerBI for the use of CNFL
      personnel.
    \end{cvitems}
  }
%---------------------------------------------------------
\cventry
  {Leading Development Technician} % Job title
  {IFAM: Expansion and improvement of the Active Mobility Index (AMI) capabilities} % Organization
  {Moravia, Costa Rica} % Location
  {2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Creation of the cartographic viewer backend.
      \item Web maps development with MapBender.
      \item ETL tasks for data integration between GIS and IMA.
      \item Training in the use of the platform.
    \end{cvitems}
  }
%---------------------------------------------------------
\end{cventries}